---
title: "Lab_8"
author: "Cooper"
date: "March 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the packages we'll need

```{r}
library(tidyverse)
library(sf)
library(tmap)
library(spatstat)
library(leaflet)
library(maptools)
```

###Column graph of Texas oil spills
```{r}
oil_spills <- read_csv("oil_spills.csv")
View(oil_spills)

df <- oil_spills %>%
  filter(`Accident State` == "TX" & `Accident Year` < 2017) %>%
  group_by(`Accident Year`)%>%
  summarise(Loss = sum(`Net Loss (Barrels)`))
df
colnames(df) <- c("Year","Loss")

ggplot(df, aes(x= Year, y = Loss)) +
  geom_col()
```

### Leaflet plot of spill locations in TX 2016
```{r}
df_loc <- oil_spills %>%
  filter(`Accident State`=="TX" & `Accident Year`==2016) %>%
  select(Latitude, Longitude, `Net Loss (Barrels)`)

colnames(df_loc) <- c("latitude", "longitude", "net_loss")

oil_sf <- st_as_sf(df_loc, coords = c("longitude", "latitude"), crs = 4326)

leaflet(oil_sf) %>% 
  addTiles() %>% 
  addMarkers()
```

## tmap plot with TX state shapefile

```{r}
states <- st_read(dsn = "." , layer = "states")

tex_border <- states %>%
  filter(STATE_NAME == "Texas") %>%
  st_transform(4326)
plot(tex_border)

tm_shape(tex_border) +
  tm_polygons()+
  tm_shape(oil_sf)+
  tm_dots(size = 0.3)
```

Convert to spatial points patterns : combination of point data and bounding window

```{r}

spill_sp <- as(oil_sf, "Spatial")
spill_ppp <- as(spill_sp, "ppp")

tx_sp <- as(tex_border, "Spatial")
tx_owin <- as(tx_sp, "owin")

all_ppp <- ppp(spill_ppp$x, spill_ppp$y, window = tx_owin)
```

###A density plot:

```{r}
plot(density(all_ppp, sigma = 0.4))
```

### Quadrat test for spatial evenness 

```{r}
oil_qt <- quadrat.test(all_ppp, nx = 5, ny = 5) #called a test for csr but really a test of evenness, so
oil_qt

plot(all_ppp)
plot(oil_qt, add = TRUE, cex = 0.4)
#conclude data are not evenly distributed#
```

### G-function for Nearest Neighbor Analysis 

```{r}
r<- seq(0,1, by = 0.01)

oil_gfun <-envelope(all_ppp, fun =Gest, r = r, nsim = 100)

ggplot(oil_gfun, aes(x = r, y = obs)) + 
  geom_line(color = "black") +
  geom_line(aes(x = r, y = theo), color = "red") #theo comes from envelope and nsim
# our data has higher proportion of point pairs with nearest neighbors at shorter distances compared to csr data => our data is more clustered
```

#Nearest neighbor using the L-function (Ripley's K but standardized)
```{r}

r2 <- seq(0,3, by = 0.5)

oil_lfun <- envelope(all_ppp, fun = Lest, r=r2, nsim =20, global = TRUE) #more computationally intensive, so use smaller nsim =>uses those increasing bubbles

ggplot(oil_lfun, aes(x=r2, y=obs))+
  geom_line(color = "black")+
  geom_line(aes(x = r2, y = theo), color = "blue")
```

